Conjure: Summoning Proxies from Unused Address Space

### 2019-09-25 paper/background.tex
minor edits from Nikita

Refraction networking operates by injecting covert communication inside a
client's HTTPS connection with a reachable site, also known as a decoy site. In
a regular HTTPS session, a client establishes a TCP connection, performs a TLS
handshake with a destination site, sends an encrypted web request, and
receives an encrypted response. In refraction routing, at least one direction
of this exchange is observed by a \emph{refraction station}, deployed at
some Internet service provider (ISP). The station watches for a covert signal from
the client that this connection is to be used for censorship circumvention.
Upon seeing the signal, the station will take over the HTTPS session,
and establish a proxy session with the client that can then be used for covert
communication.

>>>>

Refraction networking operates by injecting covert communication inside a
client's HTTPS connection with a reachable site, also known as a decoy site. In
a regular HTTPS session, a client establishes a TCP connection, performs a TLS
handshake with a destination site, sends an encrypted web request, and
receives an encrypted response. In Refraction Networking, at least one direction
of this exchange is observed by a \emph{refraction station}, deployed at
some Internet service provider (ISP). The station watches for a covert signal from
the client that this connection is to be used for censorship circumvention.
Upon seeing the signal, the station will take over the HTTPS session,
and establish a proxy session with the client that can then be used for covert
communication.

### 2019-09-25 paper/figures.tex
minor edits from Nikita

\newcommand{\FigImplementation}{
\begin{figure}[t]
    \centering
    \includegraphics[width=0.7\linewidth,clip]{figures/dark-decoy-impl1.png}
    \caption{\textbf{Station Architecture}\,---\,\rm%
        We used PF\_RING to receive packets from a 20~Gbps tap which we load balance
        across 4~CPU cores. The detector processes identify registrations, sending notification to
        all other cores via redis and to the local application 
        via ZMQ when a new registration is received . The detector also
        identifies packets associated with registered flows and diverts them
        to the local application which handles proxying connections. The local 
        application determines which transport the flow should use based on a parameter specified in
        the client's registration and initializes a goroutine to handle forwarding. 
        \\\hspace{\textwidth}
        A censor trying to interfere in this
        connection would need to take over the clients IP address in a precise window (after the 
        registration but before the client connects to the phantom) and correctly guess the phantom host's 
        IP address (or connect to all possible phantom IPs) before the active probe traffic gets to the local application. 
        At this point their connection will fail in a manor specific to the transport that the client specified
        in the registration (e.g. connecting to OSSH without knowledge of the pre-shared secret).}
    \label{fig:implementation}
\end{figure}
}

@@

    \caption{\textbf{First generation systems}\rm for Refraction Networking, such as Telex and Cirripede, operated as inline network elements, with the ability to observe traffic and block specific flows. ISPs worried that if the inline element failed, it could bring down the network.\looseness=-1}
    \label{fig:refraction-v1}
  \end{subfigure}
  \vspace{16pt}

@@

    \caption{\textbf{TapDance}\rm is a second-generation Refraction Network scheme that operates without flow blocking, needing only to passively observe traffic and inject packets. TapDance has recently been deployed at a mid-size ISP, but the techniques used to silence the decoy site and participate in the client--decoy TCP connection mid-stream add significant complexity, performance bottlenecks, and detection risk.}
    \label{fig:tapdance}
  \end{subfigure}
  \vspace{16pt}

>>>>

\newcommand{\FigImplementation}{
\begin{figure}[t]
    \centering
    \includegraphics[width=0.7\linewidth,clip]{figures/dark-decoy-impl1.png}
    \caption{\textbf{Station Architecture}\,---\,\rm%
        We used PF\_RING to receive packets from a 20~Gbps tap which we load balance
        across 4~CPU cores. The detector processes identify registrations, sending notification to
        all other cores via redis and to the local application 
        via ZMQ when a new registration is received . The detector also
        identifies packets associated with registered flows and diverts them
        to the local application which handles proxying connections. The local 
        application determines which transport the flow should use based on a parameter specified in
        the client's registration and initializes a goroutine to handle forwarding. 
        \\\hspace{\textwidth}
        A censor trying to interfere in this
        connection would need to take over the clients IP address in a precise window (after the 
        registration but before the client connects to the phantom) and correctly guess the phantom host's 
        IP address (or connect to all possible phantom IPs) before the active probe traffic gets to the local application. 
        At this point their connection will fail in a manner specific to the transport that the client specified
        in the registration (e.g. connecting to OSSH without knowledge of the pre-shared secret).}
    \label{fig:implementation}
\end{figure}
}

@@

    \caption{\textbf{First generation systems}\rm\ for Refraction Networking, such as Telex and Cirripede, operated as inline network elements, with the ability to observe traffic and block specific flows. ISPs worried that if the inline element failed, it could bring down the network.\looseness=-1}
    \label{fig:refraction-v1}
  \end{subfigure}
  \vspace{16pt}

@@

    \caption{\textbf{TapDance}\rm\ is a second-generation Refraction Network scheme that operates without flow blocking, needing only to passively observe traffic and inject packets. TapDance has recently been deployed at a mid-size ISP, but the techniques used to silence the decoy site and participate in the client--decoy TCP connection mid-stream add significant complexity, performance bottlenecks, and detection risk.}
    \label{fig:tapdance}
  \end{subfigure}
  \vspace{16pt}

### 2019-09-25 paper/paper.tex
minor edits from Nikita

%Importance of Refraction Networking
%-what it is, how it solves many of the above problems
%-acknowledge challenge of ISP deployment, cite TapDance deployment as only refraction technology that has overcome this challenge so far
A family of techniques called Refraction Networking~\cite{telex11,cirripede11,curveball11,tapdance14,rebound15,slitheen16,waterfall17}, formerly known
as Decoy Routing, has made promising steps towards that goal.
These techniques operate in the network's core, at cooperating Internet Service Providers
(ISPs) outside censoring countries~\cite{refraction-site}.  Clients access circumvention services by connecting to a ``decoy site''---any uncensored website for which the connection travels over a participating ISP\@.  Upon recognizing a steganographic signal from the client, the ISP modifies the connection response to return censored content requested by the user.
Censors cannot easily block access without also blocking legitimate connections to the decoy sites---collateral damage that may be prohibitive for censors if Refraction is widely deployed~\cite{robinson2013collateral}.

@@

We introduce the \scheme protocol (Section~\ref{sec:architecture})
and analyze its security, finding that it resists a broader
range of detection attacks than TapDance.
We have implemented \scheme (Section~\ref{sec:implementation})
and deployed it on a 20~Gbps ISP testbed similar to the TapDance
deployment~\cite{frolov2017isp}.  Compared to TapDance, we find that
\scheme has reduced complexity and substantially improved performance
(Section~\ref{sec:evaluation}): on average, \scheme has 20\% lower latency,
14\% faster download bandwidth, and over 1400 times faster upload bandwidth.
In addition, \scheme provides significantly
more flexibility than existing Refraction protocols, allowing maintainers to
respond to future censor techniques.
We believe that these advantages
make \scheme a strong choice for future Refraction Networking deployments.

@@

We assume that the censor can know what network the \scheme station(s) are
deployed in and the prefixes phantom hosts are selected from, but that blocking those
networks outright brings a collateral
damage the censor is unwilling to suffer. Instead, the censor aims to identify
the addresses that are phantom hosts, and block only those. We note this
assumption supposes that the deployment is large enough to deter routing around
decoy attacks~\cite{rad12,true-cost-rad}.

@@

Similar to previous schemes, our design does not require expensive in-line
flow blocking and is accomplished with only a passive tap at the ISP, imparting
little to no burden on their infrastructure and service reliability.
Our architecture is also modular, in that the registration and connection steps operate
independently, allowing a wide range of flexibility to evade censors. We
describe each of these components, and then describe our implementation and
deployment in Section~\ref{sec:implementation}.

@@

Once the phantom host IP address has been selected, the station watches for
packets with the source address of the original client and the phantom as the destination, 
and forwards them on to the a local application handling transports. The station only 
forwards packets that originate from the IP address of the registering client, making the
 phantom host appear firewalled off to everyone but the client.
We note that censors have been observed taking over client IP
addresses for follow-up probing~\cite{ensafi-tor}. This would allow censors to
hijack registrations if they can connect within the small window between client 
registration and connection. However this only 
allows the censor to communicate to the local application that handles transports, 
it does not connect them to the covert address that the client indicated in their registration. 
Filtering by client IP and phantom IP also prevents censors from enumerating the
address space before hand, as they would have to do so from every potential
client IP address. Simply scanning the prefixes with ZMap~\cite{zmap13} from a
single vantage point would not reveal hosts that only respond to specific IPs
(e.g. firewalled subnets).

@@

However, there are proposals to encrypt the SNI in the Client Hello~\cite{ietf-tls-esni-02},
though none have been implemented or deployed as of 2019. Nonetheless,
if widely adopted, Encrypted SNI (ESNI) would offer a powerful solution for
\scheme applications by allowing the client to use plain TLS as the transport
while remaining hidden from the censor.
Censors could still try to actively probe with guesses for the SNI,
servers could respond with generic ``Unknown SNI'' errors. If such responses
were common for incorrect SNI, the censor's efforts to identify phantom hosts
would be frustrated.

@@

\textit{Nearby sites --} pick websites that are
legitimately hosted in or near the network of the phantom host addresses
effectively creating copies of legitimate sites. However, other signals such as 
DNS may reveal the true mask site.

\textit{Popular sites --} choose mask sites from a list such as the Alexa
top site~\cite{alexa-top500} list. Although it may be wise to avoid
sites that are obviously not hosted in the phantom host address range, such as
large companies that run their own data centers and own their own ASN.
The list could also be filtered to domains that resolve to different IP
addresses from different vantage points, making it harder for a censor to know
if a phantom host corresponds to a domain's IP.

\textit{Passive observation --} collect sites by passively observing DNS requests, TLS
SNI, or certificates that pass by at the network tap. This would allow for building a realistic set
of sites that are plausibly in the vicinity of the phantom host addresses
that pass by the tap.

>>>>

%Importance of Refraction Networking
%-what it is, how it solves many of the above problems
%-acknowledge challenge of ISP deployment, cite TapDance deployment as only refraction technology that has overcome this challenge so far
A family of techniques called Refraction Networking~\cite{telex11,cirripede11,curveball11,tapdance14,rebound15,slitheen16,waterfall17}, formerly known
as Decoy Routing, has made promising steps towards that goal.
These techniques operate in the network's core, at cooperating Internet Service Providers
(ISPs) outside censoring countries~\cite{refraction-site}.  Clients access circumvention services by connecting to a ``decoy site''---any uncensored website for which the connection travels over a participating ISP\@.  Upon recognizing a steganographic signal from the client, the ISP modifies the connection response to return censored content requested by the user.
Censors cannot easily block access without also blocking legitimate connections to the decoy sites---collateral damage that may be prohibitive for censors if Refraction Networking is widely deployed~\cite{robinson2013collateral}.

@@

We introduce the \scheme protocol (Section~\ref{sec:architecture})
and analyze its security, finding that it resists a broader
range of detection attacks than TapDance.
We have implemented \scheme (Section~\ref{sec:implementation})
and deployed it on a 20~Gbps ISP testbed similar to the TapDance
deployment~\cite{frolov2017isp}.  Compared to TapDance, we find that
\scheme has reduced complexity and substantially improved performance
(Section~\ref{sec:evaluation}): on average, \scheme has 20\% lower latency,
14\% faster download bandwidth, and over 1400 times faster upload bandwidth.
In addition, \scheme provides significantly
more flexibility than existing Refraction Networking protocols, allowing maintainers to
respond to future censor techniques.
We believe that these advantages
make \scheme a strong choice for future Refraction Networking deployments.

@@

We assume that the censor can know what network the \scheme station(s) are
deployed in and the prefixes phantom hosts are selected from, but that blocking those
networks outright brings a collateral
damage the censor is unwilling to suffer. Instead, the censor aims to identify
the addresses that are phantom hosts, and block only those. We note this
assumption supposes that the censor does not mount effective routing
decoy attacks~\cite{rad12,true-cost-rad}; we discuss these attacks further in Section~\ref{sec:placement-rad}.

@@

Similar to TapDance~\cite{tapdance14}, our design does not require expensive in-line
flow blocking and is accomplished with only a passive tap at the ISP, imparting
little to no burden on their infrastructure and service reliability.
Our architecture is also modular, in that the registration and connection steps operate
independently, allowing a wide range of flexibility to evade censors. We
describe each of these components, and then describe our implementation and
deployment in Section~\ref{sec:implementation}.

@@

Once the phantom host IP address has been selected, the station watches for
packets with the source address of the original client and the phantom as the destination, 
and forwards them on to the a local application handling transports. The station only 
forwards packets that originate from the IP address of the registering client, making the
 phantom host appear firewalled off to everyone but the client.
We note that censors have been observed taking over client IP
addresses for follow-up probing~\cite{ensafi-tor}. This would allow censors to
hijack registrations if they can connect within the small window between client 
registration and connection. However this only 
allows the censor to communicate to the local application that handles transports, 
it does not connect them to the covert address that the client indicated in their registration. 
Filtering by client IP and phantom IP also prevents censors from enumerating the
address space before hand, as they would have to do so from every potential
client IP address. Simply scanning the prefixes with ZMap~\cite{zmap13} from a
single vantage point would not reveal hosts that only respond to specific IPs
(e.g., firewalled subnets).

@@

However, there are proposals to encrypt the SNI in the Client Hello~\cite{ietf-tls-esni-02},
though none have been implemented or deployed as of 2019. Nonetheless,
if widely adopted, Encrypted SNI (ESNI) would offer a powerful solution for
\scheme applications by allowing the client to use plain TLS as the transport
while remaining hidden from the censor.
Censors could still try to actively probe with guesses for the SNI,
but servers could respond with generic ``Unknown SNI'' errors. If such responses
were common for incorrect SNI, the censor's efforts to identify phantom hosts
would be frustrated.

@@

\textit{Nearby sites ---} pick websites that are
legitimately hosted in or near the network of the phantom host addresses
effectively creating copies of legitimate sites. However, other signals such as 
DNS may reveal the true mask site.

\textit{Popular sites ---} choose mask sites from a list such as the Alexa
top site~\cite{alexa-top500} list. Although it may be wise to avoid
sites that are obviously not hosted in the phantom host address range, such as
large companies that run their own data centers and own their own ASN.
The list could also be filtered to domains that resolve to different IP
addresses from different vantage points, making it harder for a censor to know
if a phantom host corresponds to a domain's IP.

\textit{Passive observation ---} collect sites by passively observing DNS requests, TLS
SNI, or certificates that pass by at the network tap. This would allow for building a realistic set
of sites that are plausibly in the vicinity of the phantom host addresses
that pass by the tap.
